Reconstructing Propositional Proofs in Type Theory

### 2017-10-27 paper/sections/metis-language-and-proofs.tex
[ paper ] metis rules improved.

In the following table we present the list of inference rules used by \Metis in
the \TSTP derivations for propositional logic and reconstructed in
Section~\ref{sec:proof-reconstruction} . The reader may notice that the
inference rules presented in Fig~\ref{fig:metis-inferences} diverge from the
rules in Table~\ref{tab:agda-metis-table}. However, the former rules are
implemented by the rules in the latter. For instance, as far as we know, in
\TSTP derivations, \canonicalize, \clausify, \conjunct, and \simplify, are all
rules that represent the \emph{axiom} rule in the \Metis rules.

In the aforementioned table, we first present
the \strip inference rule since it is the rule that appears first after each
conjecture. The other rules are sorted mainly follow their level of complexity
of their definitions and the formalization presented in
Section~\ref{ssec:emulating-inferences}. Some inference rules depends the
formalizations of other rules. For instance, the \simplify rule and the
\clausify rule  need functions
developed for the \canonicalize rule. The \canonicalize rule needs functions
developed in the \resolve section. But the \resolve rule depends on the
\conjunct rule.

>>>>

We present the list of inference rules used by \Metis in
the \TSTP derivations for propositional logic
in Table~\ref{tab:agda-metis-table}.
We reconstruct these rules in Section~\ref{sec:proof-reconstruction}.
The reader may notice that the
inference rules presented in Fig~\ref{fig:metis-inferences} diverge from the
rules in aforementioned table. However, the former rules are
implemented by the latter rules. For instance, as far as we know, in
\TSTP derivations, \canonicalize, \clausify, \conjunct, and \simplify, are all
rules that represent the \emph{axiom} rule by \Metis.

We first present the \strip inference rule since it is the rule that appears
first after each conjecture. The other rules are sorted mainly follow their
level of complexity of their definitions and the formalization presented in
Section~\ref{ssec:emulating-inferences}. Some inference rules depends the
formalizations of other rules. For instance, the \simplify rule and the
\clausify rule  need functions developed for the \canonicalize rule. The
\canonicalize rule needs functions developed in the \resolve section. But the
\resolve rule depends on the \conjunct rule.
